\Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project

### 2014-06-12 articles/2014/whisper/aricleEbauche/articleIrodsUserMeeting.tex
finish first version of Whisper use case subsection

\section{Software for data-intensive processing (6-12\S , 1-2 pages) }
~\\

@@

	\begin{enumerate}
	  \item Scientific whisper results: theses, articles, prices
  	  \item Organisation with a DataSet: Evaluation local/Ciment, capacities adaptation students
  	  \item Comparison data management, example Japan processing/USArray 
  	  \item Evolution specification, genericty of the codes, degree of automatization
  	  \item First step: Conversion data format, distributions of datas on ressources: decrease the concurrency
  	  \item Back to the first package signal processing for Japan
  	  \item Identification seismogram: Dates, stations  / Modelization distribution: sublist Dates, Stations
  	  \item Adding python modules for data retrieve + Calls.
  	  \item Focus on encapsulation queries
      \item The file parameters
      \item the file start.bash
      \item The jdl file
  	  \item Back to the package correlation: similar adds 
  	  \item Focus on the distribution problem (Space complexity/Transfer)
  	  \item Mode besteffort: increase of datas transfert, it possibly adds also new steps of data storage.
  	  \item Some order of magnitude for the Japan Computation.
  	  \item On the Japanese results.
  	\end{enumerate}

@@

Most of the time, on the computer part, the approach with researchers is as follows.
After retrieving data from a data center or directly between person, we have to assess how this data can be processed.
According to the computing time and storage capacity, either we perform operations on a dedicated bay (also host by Ciment), or either we use the Ciment infrastructure.
It depends also on the ease of computer users and most of the time, at least the last treatments (less computationally expensive) are made locally
(Some IT codes are also provided in order to retreive results on distributed storage).

@@

The mode besteffort also increase the transfert of data because some job are killed and submit in an other place.
Moreover in some cases, such that a big walltime, we add new steps of iRODS storage for the process in order to store intermediate calculation
(It is not the case for correlation because of the good granularity). 
Note that this may represent a significant development effort.

>>>>

\section{Software for data-intensive processing (6-12\S , 1-2 pages) } \label{Section_Software_for_data-intensive_processing}
~\\

@@

	\begin{enumerate}
	  \item Scientific whisper results: theses, articles, prices
  	  \item Organisation with a DataSet: Evaluation local/Ciment, capacities adaptation students
  	  \item Comparison data management, examples Japan processing/USArray 
  	  \item Evolution specification, genericty of the codes, degree of automatization
  	  \item First step: Conversion data format, distributions of datas on ressources: decrease the concurrency
  	  \item Back to the first package signal processing for Japan
  	  \item Identification seismogram: Dates, stations  / Modelization distribution: sublist Dates, Stations
  	  \item Adding python modules for data retrieve + Calls.
  	  \item Focus on encapsulation queries
      \item The file parameters
      \item the file start.bash
      \item The jdl file
  	  \item Back to the package correlation: similar adds 
  	  \item Focus on the distribution problem (Space complexity/Transfer)
  	  \item Focus on file size: flat/dictionnary
  	  \item Mode besteffort: increase of datas transfert, it possibly adds also new steps of data storage.
  	  \item Some order of magnitude for the Japan Computation.
  	  \item On the Japanese results.
  	\end{enumerate}

@@

Most of the time, on the computer part, the approach with researchers is as follows.
After retrieving data from a data center or directly between person, we have to assess how this data can be processed.
According to the computing time and storage capacity, either we perform operations on a dedicated bay (also host by Ciment), or either we use the Ciment infrastructure.
It depends also on the ease of computer users and most of the time, at least the last treatments (less computationally expensive) are made locally
(Some IT codes are also provided in order to retreive results on distributed storage).
For instance, with small datasets (datas from La Reunion or the Alpes) we work only locally. With larger dataset (China, USArray, Japan Network).
We use both local and distributed computation.

@@

Moreover, special attention was given to selecting the size of files to transfer with iRODS.
We do not store each correlation separately, we group them into dictionary to achieve file sizes between 100MB and 500MB most of the time. 
This order of magnitude seems appropriate for the infrastructure iRODS.
For simplicity, we build the grouping according to the parameters of the distribution. This allows to improve the transfer performance.
However, unlike a flat architecture, this forced us to develop codes to retrieve the data. Analysis of some subset of correlations (the 3rd step of the figure \ref{whisperGeneralWorflow}) may request transfer much more than desired.

The mode besteffort also increases the transfert of data because some job are killed and are submitted in an other place.
Moreover in some cases, such that a big walltime, we add new steps of iRODS storage for the process in order to store certain intermediate calculation
(It is not the case for the correlations because of the good granularity). Note that this may represent a significant development effort.

We focus now on the Japanese computation. With the optimizations described in section \ref{Section_Software_for_data-intensive_processing} 
and the data-grid environment, the computation of 350 millions individual correlations of the Japanese Network (especially the dense Hi-Net Network). 
are done at most a few days. This is a big change that can test many treatments in order to find information in the noise.
More precisely the seismogram processing of the Japanese network take half day here (depend obiously on the resampling).
Depending on the types of the correlations (stacking, overlap) and also of the availability of the grid (we suppose an usual case here), 
the computation of all the correlations take between 9h and 20h. The 'iget' i-commands corresponds approximatively to 11TB (with the best-effort mode,
some transfers are carried out several times) whereas the 'iput' i-command corresponds here to 3.3TB.

We illustrate with the figure \ref{JapanVelocity}, one of the analysis of the correlations that represents an image
of change of the velocity of seismic waves.
\begin{center}%[h]
\centering
\captionof{figure}{\label{JapanVelocity}}
\includegraphics[width=8cm]{JapanVelocity.png}
\end{center}
